Gaudeamus 2017 Figures

### 2018-02-16 inst/examples/201705-Gaudeamus.Rmd
ok

```{r Gaudeamus-lineplot, message=FALSE, warning=FALSE, fig.width=10, fig.height=3, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, color = catalog)) + 
       geom_point() + 
       geom_line() + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) +
       guides(color = guide_legend(reverse = TRUE, title = "")) #+ 
print(p)

```

@@

>>>>

@@

  # df2$gatherings
